---
title: 'MB AtHome: LWL stimuli AoA Calculation: Italian'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

# Constraints

For the nouns:

* 4 of the nouns should be acquired early (AoA around 12 months)
    + 2 nouns should come from the category "body_parts"
    + 2 nouns should come from the category "food_drink"
* 4 of the nouns should be acquired late (AoA around 18 months)
    + 2 nouns should come from the category "body_parts"
    + 2 nouns should come from the category "food_drink"

For the verbs:

* 2 of the verbs should be acquired early (AoA around 12 months)
* 2 of the verbs should be acquired early (AoA around 18 months)


Language specific constraints concerning target-distractor pairs:

* Nouns should be paired with nouns and verbs paired with verbs
* Early nouns should be paired together, late nouns should be paired together (e.g. early body_parts paired with early food_drink)
* Early verbs should be paired together, late verbs should be paired together
* Pairs should have the same grammatical gender if your language uses determiners that mark grammatical gender (e.g., la/le in French); 
* Pairs should not start with the same phoneme

# Find Language in wordbankr

```{r packages}

# R version 4.1.0 (2021-05-18) -- "Camp Pontanezen"

library(wordbankr)
library(dplyr)
library(tidyr)
library(purrr)
library(stringi)
library(kableExtra)

```

```{r echo = FALSE}

gi <- get_instruments()

gi %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```

# Italian


```{r German}

wordbank_lang <- "Italian"

source("scripts/wordbank.R")

```


## Choosing the Nouns

### Body Parts

```{r echo = FALSE}

body_parts %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```

#### Early AoA



#### Late AoA



### Food Drink

```{r echo = FALSE}

food_drink %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA



#### Late AoA




## Choosing the Verbs


```{r echo = FALSE}

verbs %>% 
  arrange(Wordbank_AoA_understands)  %>% 
  kable %>%
  kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "750px", height = "250px")

```


#### Early AoA




#### Late AoA




## Target-Distractor pairs

### Nouns

#### Early AoA:


#### Late AoA:



### Verbs


## Final List




