---
title: 'MB AtHome: LWL stimuli search'
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# R version 4.1.0 (2021-05-18) -- "Camp Pontanezen"

library(wordbankr)
library(childesr)
library(dplyr)

```


Principled way of doing this:

- first, check if there is wordbank data
  - if so, use this as the "founding" set of words to look through
  - is not, then look for an internally provided set of words (csv file)
          try looking for Dutch info in the manybabies1-CDI project (otherwise this is currently not public)
  
- extract any information from the wordbank data we may want
  - age at which 50% is achieved for comprehension
  - age at which 50% is achieved for production

- then, token frequency in CHILDES

- then peekbank data (only works for English now)



```{r English_American}

# first, identify the strings used for this language

#Wordbank
# get_instruments()
wordbank_lang <- "English (American)"


# CHILDES
# uses the collection names listed here: https://childes.talkbank.org/access/
childes_lang <- "Eng-NA"






```

