---
title: 'MB AtHome: LWL stimuli AoA Calculation'
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# R version 4.1.0 (2021-05-18) -- "Camp Pontanezen"

library(wordbankr)
library(dplyr)
library(tidyr)
library(purrr)
library(stringi)

```

# Explanation

This script is designed to aid the MB-AH LWL project researchers in choosing target words to test in each language. It relies on the age of acquisition data calculated by Wordbank in available languages. 

We focus first on stimuli selection for infants under 18 months. For each language, we would like to select 10 words, consisting of 8 nouns (4 pairs of 2) and 4 verbs (2 pairs of 2). This approach assumes that words will vary across languages, while strictly controlling for estimated age of acquisition (AoA). The measure of AoA that we use is the age at which 50% of children are estimated to understand the word. It will also control for semantic categories, 

For the nouns:
- 4 of the words should be acquired early (AoA around 12 months)
- 4 of the words should be acquired later (AoA around 18 months)

```{r word_list}

# 39 chosen words

word_list <- c("drink (action)",
      "eat",
      "hug",
      "kiss",
      "play",
      "point",
      "sit",
      "sleep",
      "stand",
      "bird",
      "cow",
      "dog",
      "duck",
      "fish (animal)",
      "frog",
      "horse",
      "lion",
      "monkey",
      "foot",
      "hand",
      "shoe",
      "sock",
      "apple",
      "banana",
      "carrots",
      "cookie",
      "juice",
      "milk",
      "bottle",
      "cup",
      "spoon",
      "baby",
      "ball",
      "book",
      "cat",
      "boat",
      "car",
      "train",
      "truck"
)

w.list <- as.data.frame(word_list)
w.list$order <- rownames(w.list)

w.list$definition <- sub("* \\(.*\\)", "", w.list$word_list)

#w.list$definition <- tolower(w.list$definition)


```



```{r set_languages}

# Based on the language being investigated, change these variables!

# wordbank
#  [1] "British Sign Language"  "Cantonese"              "Croatian"              
#  [4] "Danish"                 "English (American)"     "German"                
#  [7] "Hebrew"                 "Italian"                "Mandarin (Beijing)"    
# [10] "Norwegian"              "Russian"                "Spanish (Mexican)"     
# [13] "Swedish"                "Turkish"                "French (Quebecois)"    
# [16] "Slovak"                 "English (British)"      "American Sign Language"
# [19] "Greek (Cypriot)"        "Kigiriama"              "Kiswahili"             
# [22] "Czech"                  "English (Australian)"   "Latvian"               
# [25] "Korean"                 "French (French)"        "Spanish (European)"    
# [28] "Portuguese (European)"  "Mandarin (Taiwanese)" 

#wordbank_lang <- "English (American)"
#wordbank_lang <- "German" # no comprehension data, so takes AoA here from production, as of May 3, 2022
#wordbank_lang <- "Spanish (European)" # no uni_lemma as of May 3, 2022

wordbank_lang <- "Spanish (Mexican)"

# CHILDES
#  [1] "Frogs"          "Eng-NA"         "Scandinavian"   "Spanish"        "French"        
#  [6] "DutchAfrikaans" "Chinese"        "Other"          "Japanese"       "Romance"       
# [11] "Clinical"       "Eng-UK"         "Celtic"         "EastAsian"      "Slavic"        
# [16] "German"         "Clinical-MOR"   "Biling"         "XLing"          "Dutch"  

# childes_lang <- "Eng-NA"
#childes_lang <- "German"
childes_lang <- "Spanish"

```







```{r template}

# query Wordbank 
source("scripts/wordbank.R")
# returns aoa.m, a summary of youngest reported AoA for understanding and producing
# returns list_de_mot, a list of the language-specific (!) words in aoa.m to be used for querying CHILDES

# query CHILDES
# using the definition words identified in the last step
# this helps ensure translations show up correctly


# then, query childes
source("scripts/childes.R")
# returns prod_stats, a summary of the token frequency of the words in word_list




# skipping Peekbank for now, since its not available in many languages, but see:
# source("scripts/peekbank.R")
# for a code of how to calculate item difficulty
# in case more languages are added in the future







# Combine the Wordbank and CHILDES data together
# if CHILDES doesn't produce any data, then return just Wordbank data, with NA's in the CHILDES column

if(nrow(prod_stats) != 0 & nrow(aoa.m) != 0){
d <- left_join(aoa.m, prod_stats, by = c("definition" = "gloss"))
} else if(nrow(prod_stats) == 0){
  d <- aoa.m
  d$CHILDES_token_freq <- NA
} else {
    d <- prod_stats
  d$Wordbank_AoA_understands <- NA
  d$Wordbank_AoA_produces <- NA
}



# write into their own csv file
# which can be later edited to add additional information
vs_filename <- paste0("data/", wordbank_lang, "_vocab_data.csv")  

write.csv(d, file = vs_filename)


```








